Drug sensitivity prediction with normal inverse Gaussian shrinkage informed by external data

### 2020-02-06 docs/supplement1.Rnw
small changes

>>>>

	\section{Jeffrey's prior}
	We parametrise the data with a Gaussian distribution with unknown mean and 
	variance, i.e., $y_i \sim \mathcal{N} (\mu, \sigma^2)$. This gives us the
	following Hessian (matrix of second derivatives) of the log density:
	$$
	\mathbf{H}(\log f(y_i | \mu, \sigma^2)) = \begin{bmatrix}
	-\frac{1}{\sigma^2} & y_i - \mu \\
	y_i - \mu & \frac{1}{2\sigma^4} - \frac{(y_i - \mu)^2}{\sigma^6}.
	\end{bmatrix}
	$$
	Jeffrey's prior is now found as:
	$$
	\pi(\mu, \sigma^2) \propto |\mathcal{I}(\mu, \sigma^2)|^{1/2} = 
	|-\E (\mathbf{H})|^{1/2} = \begin{vmatrix}
	\frac{1}{\sigma^2} & 0 \\
	0 & \frac{1}{2\sigma^4}
	\end{vmatrix}^{1/2} \propto 1/\sigma^3,
	$$
	where $\mathcal{I}(\theta)$ denotes the Fisher information of $\theta$.
